% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2017 Jason R. Blevins <jrblevin@sdf.org>
% http://jblevins.org/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass{article}

\def\name{Louis Viot}

\usepackage[utf8]{inputenc}                       
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{mathpazo}

\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {applied mathematics, computer science},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

\renewenvironment{itemize}{
  \begin{list}{}{
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0.25em}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0.25em}
    }
}{
  \end{list}
}

\setlength\parindent{0em}

\renewcommand{\today}{\ifcase \month \or January\or February\or March\or April\or May \or June\or July\or August\or September\or October\or November\or December\fi \space \the\year}

\begin{document}

{\huge \bf \name}

\bigskip
\today

\bigskip
\begin{minipage}[t]{0.495\textwidth}
	30 Avenue Henri Pontier \\
    Building C2 \\
    Aix-en-Provence, 13100 France
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Phone: 0033628685904 \\
  Email: \href{mailto:louis.viot@alumni.enseeiht.fr}{louis.viot@alumni.enseeiht.fr} \\
\end{minipage}

\section*{Education}

\begin{itemize}
  	\item \textbf{PhD in Computer Science and Applied Mathematics, 2015 - Current, CEA Cadarache, France.}
		\begin{itemize}
			\item PhD Title : ``Modeling and simulation of complex systems for nuclear severe accidents''.
			\item Supervisor : Florian De Vuyst, ENS Cachan CMLA, CNRS UMR 8536.
			\item Expecting to graduate in 2018
		\end{itemize}
	\item \textbf{MSc in Distributed Systems and Critical Software, 2014 - graduated in 2015, Toulouse, France.}
		\begin{itemize}
			\item Courses included distributed system, grid computing, distributed computing, cloud computing.
		\end{itemize}
    \item \textbf{INP ENSEEIHT, a top ranking French engineering school, 2012 - graduated in 2015, Toulouse, France.}
		\begin{itemize}
			\item Institute of Engineering in Electrical Engineering, Automation, Electronics, Computer Science, Applied Mathematics, Hydraulics, Telecommunications.
			\item Engineering Degree in Applied Mathematics and Computer Science.
			\item Courses included Optimization, Topology, Linear Algebra, Differential equation, Measure and distribution, Numerical analysis, Imperative, Functional and Object-oriented Programming, Computer architecture, Parallel algorithms.
		\end{itemize}
	\item \textbf{Classes préparatoires (MPSI, MP*), 2010 - graduated in 2012, Lycée Clemenceau, Reims, France.}
		\begin{itemize}
			\item Two years of intense preparation for selective entrance to engineering schools.
			\item Courses included : Mathematics and Physics.
		\end{itemize}
	\item \textbf{Baccalaureat S, 2007 - graduated in 2010, Lycée François Bazin, Reims, France.}
		\begin{itemize}
			\item Passed with distinction, equivalent to A levels in science
		\end{itemize}
\end{itemize}

\section*{Employment}
\begin{itemize}
	\item \textbf{Six months research internship, 2015, CEA Cadarache, France.}
		\begin{itemize}
			\item Implementation of a predictor/corrector numerical scheme in a code (\textit{Java}) for nuclear reactor severe accidents.
		\end{itemize}
	\item \textbf{Two months research internship, 2014, Polytechnic Institute, Bragança, Portugal.}
		\begin{itemize}
			\item Teeth extraction from dental x-ray using contour detection, image segmentation, texture pattern recognition and Chan-Vese active contour methods.
		\end{itemize}
	\item \textbf{Summer jobs, 2010-2013}
		\begin{itemize}
			\item Conforama, Charleville-Mézières.
			\item SCEA Les Cressonières d'Aquitaine, farming sector, Agen.
		\end{itemize}
\end{itemize}  

%\section*{Publications and Conference Papers}

%\section*{Conferences and Seminars}

\section*{Summer schools}

\section*{Programming Skills}
\begin{itemize}
	\item Operating systems : UNIX (Linux), Windows and Mac OS.
	\item Programming : C, C++, Python, Java, Fortran, OcamL, Haskell, ADA, Prolog, MatLab, Maple, \LaTeX. 
\end{itemize}  

\section*{Spoken Languages}
\begin{itemize}
	\item French : mother tongue.
	\item English : upper-intermediate level, fluent in written and spoken. Score TOEIC : 975.
	\item Russian, German : beginner.
\end{itemize}
\section*{Interests and additional information}
\begin{itemize}
	\item Sports : Cycling, Mountain Bike, Rugby.
	\item Reading and Writing : winner of the ``Etonnants-voyageur'' prize for young writers in 2008.
\end{itemize}  

\end{document}
 

